### 2013-09-18 chi2014/goals.tex
Goals: brainstorming metrices
Little wordplay

To characterize brainstorming in microtask marketplaces, we are interested in modeling the following quantities:
\begin{itemize}
\item the rate of unique idea production
\item the rate of production of unique \emph{categories} of ideas
\item the relative originality of ideas
\item individual practices in idea generation
\end{itemize}

We will examine these rates as a function of the number of ideas requested from workers.

@@

In modeling these quantities, we have several hypotheses related to results received in the aggregate (across all participants), as well as individuals' brainstorming processes.

\textbf{Hypothesis 1:} The rate of new ideas will diminish exponentially toward zero as a function of the number of responses gathered. Less formally, by continually soliciting solutions, we will eventually reach a saturation point at which any idea a worker submits is likely to be the same or practically identical to previously seen solutions. Related to this, we expect the number of \emph{categories} of ideas to diminish exponentially as well.

\textbf{Hypothesis 2:} The rate of new ideas will tend toward zero faster in some conditions than others. In particular, we expect conditions requesting a smaller number of ideas will tend toward zero faster, for reasons hypothesized next.

\textbf{Hypothesis 3:} We anticipate there is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition. In other words, we expect there to be a relatively fixed set of ideas that ``everyone'' thinks of first.

Parnes et al \cite{parnes_effects_1961} showed that more high quality ideas are generated in the latter half of a brainstorming run than the former half. Because of the difficulty in reliably assessing the quality of an idea for a brainstorming exercise, we instead consider the o-score of an idea to indirectly measure this concept.

\textbf{Hypothesis 4:} Ideas generated in the second half of a brainstorming session have higher o-scores than ideas generated in the first half.

With respect to individual brainstorming processes, we have several hypotheses derived from Nijstad and Stroebe's work and their SIAM model \cite{nijstad_how_2006}:

\textbf{Hypothesis 5:} An idea from one semantic category of ideas should more often be followed by an idea from the same category than expected by random chance.

\textbf{Hypothesis 6:} The time it takes to generate an idea should be longer when changing semantic categories than when generating ideas within a category.

>>>>

% Researchers have long debated how to best assess creativity in a way that consistently captures the complex dimensions of creativity [35]. The most commonly adopted approach [1, 5, 17] and the one we employ is to ask domain experts to subjectively make scale-rated assessments of creativity. Typically, domain experts rate originality, feasibility, elaboration, and flexibility and count the number of ideas generated [3].

To characterize brainstorming in microtask marketplaces, we are interested in modeling rates at which ideas and idea categories are generated, the originality of ideas as measured by o-scores, and individuals' idea generation processes.

@@

In modeling these quantities, we wish to explore the following hypotheses:

\textbf{Hypothesis 1:} The probability that an idea is novel decreases non-linearly as a function of the number of responses received. Similarly, we expect the rate of new idea categories to decrease non-linearly over time.

\textbf{Hypothesis 2:} There is a set of general, common ideas that make up the first several responses of every crowd brainstorming session. In other words, we expect there to be a relatively fixed set of ideas that most people think of first.

%Parnes et al \cite{parnes_effects_1961} showed that more high quality ideas are generated in the latter half of a brainstorming run than the former half. Because of the difficulty in reliably assessing the quality of an idea for a brainstorming exercise, we instead consider the o-score of an idea to indirectly measure this concept.

\textbf{Hypothesis 3:} O-scores generated in the second half of a brainstorming session will be higher than ideas generated in the first half. This hypothesis provides a complementary perspective to the former.

With respect to individual brainstorming processes, we have a pair of hypotheses derived from Nijstad and Stroebe's work and their SIAM model \cite{nijstad_how_2006}:

\textbf{Hypothesis 4:} An idea from one semantic category of ideas should more often be followed by an idea from the same category than expected by random chance.

\textbf{Hypothesis 5:} The time it takes to generate an idea should be longer when changing semantic categories than when generating ideas within a category.

### 2013-09-18 chi2014/related.tex

% TODO Note: I plaigarized the wording on these definitions from wikipedia at this point, should pull from original Osborne at some point
In the 1950s, Osborne formalized the brainstorming process, providing a set of recommendations for idea generation by groups \cite{osborn_applied_1957}: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}. These recommendations form the basis for the instructions we provide to workers in our experiments.

@@

The simplist imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated (electronic brainstorming), or those that rely on the crowd to organize or rank the ideas produced by others, as in evolutionary techniques \cite{yu_cooks_2011}.
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
In this paper, we constrain our focus to nominal brainstorming in this environment with the goal of establishing a set of baselines.

@@

In summary, while brainstorming has been examined in the traditional and electronic settings, its application in crowd marketplaces has received limited attention, leaving many open questions about how this process occurs in this environment.

>>>>

\subsection{Traditional Brainstorming}
In the 1950s, Osborne formalized the brainstorming process, providing a set of recommendations for idea generation by groups \cite{osborn_applied_1957}: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}. These recommendations form the basis for the instructions we provide to workers in our experiments.

@@

To assess the brainstorming process and its outputs, a number of measures have been proposed. Typically, the measures of concern are the novelty of generated ideas, the practicality/appropriateness of ideas, the variety of ideas (flexibility), and the quantity of ideas generated. \cite{finke1992creative, shah2003metrics}.

The most common approach to measure novelty and appropriateness is to ask domain experts to subjectively make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. Depending on the types of artifacts and researchers' interest, these two measures are sometimes combined into one measure of quality \cite{little2010exploring}.

Instead of subjective ratings, some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency with which an idea occurs, to evaluate products novelty \cite{jansson_design_1991}. We adopt this use of o-score in our later analyses.

Flexibility is often measured by the number of explored ``categories'' in a design space, or by subjective rating from domain experts \cite{lewis2011affective, marsh1996examples}. Category or feature-based quantities also yield other metrics such as within-catgories fluency and the length of train-of-thought when participants focus on a particular category \cite{nijstad_how_2006}. Building in this past line of work, we consider both individual ideas and categories of ideas.

\subsection{Crowdsourced Brainstorming}
The simplist imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated (electronic brainstorming), or those that rely on the crowd to organize or rank the ideas produced by others, as in evolutionary techniques \cite{yu_cooks_2011}.
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
In this paper, we constrain our focus to nominal brainstorming in this environment with the goal of establishing a set of baselines.

@@

In summary, while brainstorming has been examined in traditional and electronic settings, its application in crowd marketplaces has received limited attention, leaving many open questions about how this process occurs in this environment.
